\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot,
    top=2cm,
    bottom=2cm,
    left=2cm,
    right=2cm,
    footskip=1.0cm,
]{geometry}
\usepackage[explicit]{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{paracol}

% Custom Colors:
\definecolor{primaryColor}{RGB}{0, 79, 144}
\definecolor{linkBorderColor}{RGB}{0, 79, 144}

% Settings:
\pagestyle{empty}
\setlength{\parindent}{0pt}
\hypersetup{
    colorlinks=true,
    linkcolor=primaryColor,
    urlcolor=primaryColor,
    pdfborder={0 0 1 [3]}, % Customize border style
    pdfborderstyle={/S/U/W 1} % Dashed underline
}

% Section formatting:
\titleformat{\section}{
    \Large\color{primaryColor}
}{
}{
}{
    \textbf{#1}\titlerule[0.8pt]
}
\titlespacing{\section}{-1pt}{0.3cm}{0.2cm}

% Icon size adjustment:
\newcommand{\icon}[1]{{\small #1}}

\begin{document}

% Header
\begin{center}
    \fontsize{30pt}{30pt}\textbf{ALI QASEMI} \\
    \vspace{0.2cm}
    \href{mailto:Qasemi4245qq@gmail.com}{\icon{\faEnvelope[regular]} Qasemi4245qq@gmail.com} \ |
    \href{https://www.linkedin.com/in/aliqasemi/}{\icon{\faLinkedin} LinkedIn} \ |
    \href{https://github.com/aliqasemi}{\icon{\faGithub} GitHub} \ |
    \href{http://aliqasemi.github.io/}{\icon{\faLink} Personal Blog}
\end{center}

% Objective
\section{Objective}
\textit{I am seeking a backend developer position where I can contribute to the development of applications and software architecture while ensuring efficient performance. I am particularly interested in projects involving PHP Laravel and Golang.}

% Education
\section{Education}
\begin{itemize}[leftmargin=*]
    \item \textbf{Shahood University of Technology (2020 -- 2022)} \\
    Master's degree in Software Engineering \\
    Developed a tourism destination recommendation system using Python, integrating Density Means clustering and Genetic Algorithms to improve recommendation accuracy. Achieved a 28 percent improvement in precision and user satisfaction compared to traditional methods, enhancing personalization and contributing to the application of evolutionary algorithms in data-driven systems.
    \item \textbf{Shahood University of Technology (2016 -- 2020)} \\
    Bachelor of Engineering in Software Engineering
\end{itemize}


% Experience
\section{Experience}
\begin{itemize}[leftmargin=*]
    \item \textbf{Backend Developer, Willa Arts (Sep 2020 -- Aug 2022)}
    \begin{itemize}[leftmargin=1em]
        \item Designed the panel for a web builder application using PHP Laravel and Vue.js.
        \item Implemented a module enabling clients to design websites with various features.
        \item Developed a roll call system with Vue.js for the frontend and PHP Laravel for the backend.
        \item Built an LMS module for remote instruction using PHP Laravel for backend course management and Vue.js for client-side slide displays.
        \item Created a service store introducing company services with categories and features using PHP Laravel and Vue.js.
        \item Developed an audio server for podcasts and voice content with publisher features, leveraging PHP Laravel and Vue.js frameworks.
        \item Contributed to multiple modules offered as features to clients.
        \item Utilized Vue 2 and Vuex for state management, and transitioned to Vue 3 and Pinia for advanced store management.
    \end{itemize}
    \item \textbf{Backend Developer, Yasin.ai (Jun 2023 -- Nov 2024)}
    \begin{itemize}[leftmargin=1em]
        \item Led initial development of the Shia Muslim application, including backend and management panel.
        \item Designed a panel to manage texts, duas, and scriptural content categorized for immediate searching.
        \item Implemented data streaming for videos, live streams, and audio categorized and tagged for user subscriptions.
        \item Developed streaming data services using Golang and the Mux framework.
        \item I am using Go threads and a database queue for streaming data, which resulted in a 30 percent increase in streaming speed based on my setup without any server crashes.
        \item Managed application content and context with PHP Laravel.
        \item Integrated ElasticSearch for rapid and efficient content searching.
        \item Optimized application performance using Octane technology with Golang for the Laravel framework to handle high request volumes.
        \item Fully dockerized the application, including MongoDB, Octane app, MySQL, Golang, Nginx, Redis, MinIO, Prometheus, and Grafana.
        \item Created metrics for Prometheus with cache management to analyze application and user request patterns to identify areas of high interest.
        \item Enabled multilingual support across all aspects of the application, allowing dynamic addition of new languages via the management panel.
        \item Leveraged technologies such as MySQL, MongoDB, Redis caching, and Golang streaming for scalable data handling.
        \item I achieved a significant reduction in latency, improving response times from about 500ms seconds to about 150ms seconds. Additionally, I increased the request processing capability from about 120 requests per second with PHP-FPM to about 190 requests per second using Swoole, based on my setup.
    \end{itemize}
\end{itemize}

% Skills
\section{Skills}
\textbf{Programming Languages:} PHP, Golang, Python \\
\textbf{Technologies:} Laravel, MySQL, MongoDB, Docker, Redis, Minio, Vue.js, Monitoring \\
\textbf{Other:} Algorithm Design, Data Structures

% Courses
\section{Courses}
\begin{itemize}[leftmargin=*]
    \item Docker Expert at TOSINSO \\
    \href{https://tosinso.com/files/get/f6a4dee5-402f-4b49-9b25-bdc06fb2a464}{Certificate Link}
    \item Task-Oriented Course in Version Control with Git at Quera \\
    \href{https://quera.org/certificate/AMBOBgnQ/}{Certificate Link}
    \item Advanced Algorithmic Thinking and Data Structure at Quera \\
    \href{https://quera.org/certificate/qNltcusF/}{Certificate Link}
\end{itemize}

% Projects
\section{Projects}
\begin{itemize}[leftmargin=*]
    \item \textbf{Shia Muslim Application} \\
    \href{https://shiamuslimproject.com/}{shiamuslimproject.com} \ |
    \href{https://play.google.com/store/apps/details?id=com.shiamuslimproject.main}{Play Store} \ |
    \href{https://apps.apple.com/app/shia-muslim/id1613187510}{App Store}
    \item \textbf{Divine Muslim Project} \\
    \href{https://divinemuslim.com/}{divinemuslim.com} \ |
    \href{https://play.google.com/store/apps/details?id=com.divine.muslim&pcampaignid=web_share}{Play Store} \ |
    \href{https://apps.apple.com/app/divine-muslim/id6453523582}{App Store}
    \item \textbf{Willa Arts Project} \\
    \href{https://www.meshkee.com/cms-website}{cms-website}
\end{itemize}

\end{document}
